A molecular taxonomy of tumors independent of tissue-of-origin

### 2021-07-02 text/manuscript.Rmd
Update limitation of the study with model comparison result

>>>>

The outcome of our model comparison with other published classification models 
in predicting tdeath showed kNN performing slightly better. However, for the 
purpose of predicting lifetime, all models are practically equivalent. One 
explanation for this is the cluster identity does not provide much new information 
from tissue-of-origin. Most of the cluster-specific rate ($A_{cl}$) peaked around 1 for 
all models – leaving the remaining variables ($A_{0}$, $A_{r}$, and $k_{tis}$), which are 
tissue-specific, to compute tdeath. While our study focused on somatic mutations, 
the incorporation of other types of omics data may help differentiate the classes 
within cancer type. Additionally, more work in solidifying the pathway model into 
cancer hallmarks could provide biologically meaningful distinction of the clusters.
